PM Mungbean meta-analysis

### 2020-07-09 02_Preliminary_analysis.Rmd
added chunk to calculated Yield loss in Jade in 2016 experiments

>>>>

Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
```{r}
dat3 <- PM_MB_means %>%
   filter(year == "2016",
          host_genotype == "Jade",
          fungicide_ai == "control")%>%
   group_by(location)%>%
   summarise(C_Yield = mean(grain_yield.t.ha., na.rm = TRUE))

dat3$F_Yield <- PM_MB_means %>%
   filter(year == "2016",
          host_genotype == "Jade",
          fungicide_ai != "control")%>%
   group_by(location)%>%
   summarise(F_Yield = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
   pull(F_Yield)

dat3 %>% 
   mutate(diff = F_Yield - C_Yield) %>%
   mutate(percent = (diff/F_Yield)*100)
